\include{header}

\begin{document}
\title{Bilinear control theory}
\author{Uther Shackerley-Bennett}
\maketitle

\tableofcontents

\section{The Definitions}


\section{The Theorems}
$m$ denotes the number of control fields, $n$ denotes the number of modes of the system. The control functions are usually either unspecified or constrained to $u \in \mathbb{R}$. By symmetric controls I mean that the set of controls parameters is equal to its negative.

\subsection{Normal Accessibility}
$m=m$, $n=n$, any controls. Necessary and sufficient condition for control on a Lie group. p154 JurdjevicGeo or my pdf.

\subsection{Recursivity theorems}
\subsubsection{Neutrality}
$m=m$, $n=n$, any controls. Sufficient condition for control on a Lie group. Elliott p97.
\begin{itemize}
 \item Elliott contains other, equivalent definitions of neutrality.
\item I have a necessary and sufficient condition for symplectic neutrality.
\end{itemize}
\subsubsection{Genoni2012 recursivity}
$m=m$, $n=n$, any controls. It is sufficient for Lie group controllability. Note this is not as broad as the neutrality theorem above. Genoni2012.
\subsubsection{Wu non-empty set}
$m=1$, $n=1$, symmetric controls. Necessary and sufficient condition for control on a Lie group. Wu2007 and also p117 of Elliott seems to look very similar.

\subsection{Single input unbounded}
\subsubsection{Jurdjevic and Kupka sufficient condition}
$m=1$, $n=n$, unbounded controls. Sufficient condition for control on a semi-simple? Lie group. Theorem 3.11 in Elliott. Also found in Jurdjevic I think.
\begin{itemize}
 \item This seems like it must be broader than neutrality after fixing the control parameters. If this is true then neutrality is not equivalent to controllability.
\end{itemize}

\subsubsection{El-Assoudi sufficient condition}
$m=1$, $n=n$, unbounded controls. Sufficient condition for control on a semi-simple Lie group. Presumably broader than above; pretty much takes all properties of the symplectic group. ElAssoudi2014. 
\subsection{Huang's theorem}
$m=m$, $n=n$, unbounded controls. Controllability on a homogeneous space of the Lie group in infinite dimensional Hilbert space, intersected with the set of analytic vectors. Huang1983, Wu2005. 
\begin{itemize}
 \item It is the equality in the theorem that is most confusing. Why can it not be higher than the dimension of the manifold?
\end{itemize}

\subsection{Trivial theorems}
\subsubsection{Blow away the drift field}
$m>1$, $n=n$, unbounded controls. Can blow away the drift field and generate the algebra with the control fields, thus making LARC necessary and sufficient. Necessary and sufficient condition for control on a Lie group. JurdjevicGeo.
\subsubsection{Generic Generation}
$m>1$, $n=n$, unbounded controls. Can blow away the drift field. Generators are dense in the algebra and so LARC not required. JurdjevicGeo.

\section{The map of Gaussian states}
This map of bilinear control theory is applied to my map of Gaussian states. Symplectic group manifold of dimension $n(2n+1)$, symplectic vector space, metaplectic group manifold, acting on the Hilbert space with a sub-Kahler manifold: the unit sphere or projective Hilbert space in which is a sub-manifold of pure Gaussian states diffeomorphic to the open convex cone of covariance matrices in dimension $n(n+1)$.

\end{document}